\cvsection{Experience}

\begin{cventries}
  \cventry
    {Product Engineer} % Job title
    {Scale AI} % Organization
    {San Francisco, CA} % Location
    {Feb. 2021 - June 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Developed a full stack (self service) tool for customers to upload data (e.g. images, documents) and receive a labeled dataset for training their AI algorithms.  Automated assigning workers to labeling a project's data, managing their assignment with automated training courses and quality control mechanisms (using React, Node.js, and MongoDB).}
        \item {Presented system demos and provided support to customers to reach their project goals; ultimately enabling higher quality datasets for their machine learning applications.}
      \end{cvitems}
    }

  \cventry
    {Software Engineer} % Job title
    {Robotic Research LLC} % Organization
    {Gaithersburg, MD} % Location
    {June 2019 - Jan. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Supporting the development of autonomous software for the electric 
          shuttle \href{https://localmotors.com/olli}{Olli}.  Lead the deployment/mapping process for new autonomous routes \href{https://localmotors.com/deployments}{across several cities}.}
      \item {Led the creation of a web app for searching/downloading data (stored in the cloud) collected from fleets of autonomous vehicles around the world (utilizing Flask, and various AWS services).}
      \end{cvitems}
    }

  \cventry
    {Computer Vision Intern} % Job title
    {Robotic Research LLC} % Organization
    {Gaithersburg, MD} % Location
    {June 2018 - Aug. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Trained/evaluated a neural network on several datasets to perform object detection in 
photos.  Wrote Python scripts to convert various datasets into a common format for 
training.}
        \item {Created a C++ camera driver for a computer vision system in a ROS pipeline.}
      \end{cvitems}
    }

  \cventry
    {Software Developer Intern} % Job title
    {AT\&T} % Organization
    {Columbia, MD} % Location
    {May. 2017 - Dec. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Improved a network security tool by writing shell scripts to manage a Hive database built on 
top of a Hadoop Distributed File System, and by integrating a deep packet inspection C 
library into the tool.  Participated in (Agile) code reviews and sprint planning.}
      \end{cvitems}
    }

  \cventry
    {Full Stack Web Developer Intern} % Job title
    {Imaging Research Center at UMBC} % Organization
    {Baltimore, MD} % Location
    {June 2016 - Aug. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Helped develop \href{https://retrieverstories.umbc.edu}{retrieverstories.umbc.edu} (a social media site for current/former students to 
share their experiences).  Developed new features using PHP, SQL, HTML, and CSS. }
      \end{cvitems}
    }

\end{cventries}
