\cvsection{Activities \& Achievements}

% note: I prefer this look (over that of the cvskills section):
\begin{cventries}
  \cventry
    {Clubs and Volunteering:} % Job title
    % leave these 2 fields blank to nest this below RR entry above:
    {} % Organization
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Volunteered with a Gurdwara (Sikh place of worship) to help with a food drive service for people in need during Covid.}
      \item {Volunteered with the UMBC Environmental Task Force Club (cleaning up trash in the woods around campus on a weekly basis).}
      \item {Volunteered as a personal tutor for a Computer Science course.}
      \item {UMBC Hackers Club member (participated in 5 hackathon competitions).}
      \end{cvitems}
    }

  \cventry
    {Travel:} % Job title
    % leave these 2 fields blank to nest this below RR entry above:
    {} % Organization
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {I've backpacked through over 15+ countries across 4 continents while practicing languages and exchanging experiences with countless people from all over the world.  I've completed over 6 weeks of solo travel (to locations including the Amazon rainforest).}
      \item {Attended various language exchange meetups/clubs in cities across the world.}
      \end{cvitems}
    }


  \cventry
    {High School Involvement:} % Job title
    % leave these 2 fields blank to nest this below RR entry above:
    {} % Organization
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Eagle Scout (2014), National Honor Society member.}
        \item {Green Team (environmental club) Vice President, FIRST Robotics club (national championship participant).}
        \item {Varsity Volleyball and Tennis athlete.}
      \end{cvitems}
    }

\end{cventries}

\iffalse
\begin{cvskills}

  \cvskill
    {College}
    {UMBC Hackers Club member (participated in 5 hackathons), UMBC Environmental Task Force Club Member}

  %\vspace{5mm}
  \hline
  \cvskill
    {High School}
    {Eagle Scout (2014), National Honor Society member, FIRST Robotics club (national championship participant), Varsity Volleyball, Varsity Tennis.}
\end{cvskills}
\fi
