\cvsection{Experience}

\begin{cventries}
  \cventry
    {Consultant Software Engineer} % Job title
    {Robotic Research LLC} % Organization
    {Gaithersburg, MD} % Location
    {Jan. 2022 - Aug. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developing a full-stack cloud application for storing, querying, and accessing data from autonomous robotic systems.}
        \item {Developed a cloud deployment system (using terraform), allowing engineers to easily deploy the application across multiple environments.
          Created an extensive unit test system for the application, continously validating its functionality and security over time.
        }
      \end{cvitems}
    }

  \cventry
    {Founder} % Empty position
    {\href{https://global-board.org}{global-board.org}} % Project
    {Baltimore, MD} % Empty location
    {July 2021 - Present} % Empty date
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Designed and implemented a website to help users learn about every country (showing what's trending and embedding learning resources specific to each country's history, travel, and culture).  Implemented with React, Node.js, PostgreSQL, and hosted on Google Cloud.}
        \item {Using the Spotify, and Twitter APIs (to track trends across countries) and the YouTube API to automatically find the best educational videos about each country.}
        \item {Analyzing user activity over time to inform continued development of the site.}
      \end{cvitems}
    }

  \cventry
    {Product Engineer} % Job title
    {Scale AI} % Organization
    {San Francisco, CA} % Location
    {Feb. 2021 - June 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a full stack (self-service) tool for customers to upload data (e.g. images, documents) and receive a labeled dataset for training their AI algorithms.  Automated assigning workers to labeling a project's data, managing their assignment with automated training courses and quality control mechanisms (using React, Node.js, and MongoDB).}
        \item {Presented system demos and provided support to customers to reach their project goals; ultimately enabling higher quality datasets for their machine learning applications.}
      \end{cvitems}
    }

  \cventry
    {Software Engineer} % Job title
    {Robotic Research LLC} % Organization
    {Gaithersburg, MD} % Location
    {June 2019 - Jan. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Supported the development of autonomous software for the electric 
          shuttle "Olli."  Lead the deployment/mapping process for new autonomous routes across several cities.}
        \item {Led the creation of a web app for searching/downloading data (stored in the cloud) collected from fleets of autonomous vehicles around the world (utilizing Flask, and various AWS services).}
        \item {Trained a neural network to perform vehicle detection on synthetic datasets and evaluated the performance on real-world images.}
      \end{cvitems}
    }

  \cventry
    {Computer Vision Intern} % Job title
    % leave these 2 fields blank to nest this below RR entry above:
    {} % Organization
    {} % Location
    {June 2018 - Aug. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Trained/evaluated a (Mask R-CNN) neural network on several (autonomous vehicle related) datasets to perform object detection in photos and wrote Python scripts to combine various datasets into a common format for training.  Created a C++ camera driver for a computer vision system in a ROS pipeline.}
      \end{cvitems}
    }


  \cventry
    {Teaching Assistant (TA)} % Job title
    {UMBC} % Organization
    {Baltimore, MD} % Location
    {Aug. 2018 - May. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Worked as a TA for an object-oriented programming and design C++ course.  Led a weekly lab section to help students understand the week's material while evaluating their lab projects.  Helped students understand and overcome obstacles (e.g. debugging) with course projects each week during office hours and assisted the professor with grading/proctoring exams.}
      \end{cvitems}
    }

  \cventry
    {Private Tutor} % Job title
    % leave these 2 fields blank to nest this below UMBC entry above:
    {} % Organization
    {} % Location
    {Feb. 2018 - Dec. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Worked as a personal tutor for a C++ data structures course, helping students to deeply understand course concepts while fostering their ability to perform independent problem solving/learning while tackling course projects.}
      \end{cvitems}
    }

  \cventry
    {Resident Assistant (RA)} % Job title
    % leave these 2 fields blank to nest this below UMBC entry above:
    {} % Organization
    {} % Location
    {Aug. 2016 - May. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Managed a floor of ~30 students for two years and prepared educational programs related to diversity, culture, wellness, study skills, etc.}
      \end{cvitems}
    }

  \cventry
    {Software Developer Intern} % Job title
    {AT\&T} % Organization
    {Columbia, MD} % Location
    {May. 2017 - Dec. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Improved a network security tool by writing shell scripts to manage a Hive database built on 
top of a Hadoop Distributed File System, and by integrating a deep packet inspection C 
library into the tool.  Participated in (Agile) code reviews and sprint planning.}
      \end{cvitems}
    }

  \cventry
    {Full Stack Web Developer Intern} % Job title
    {Imaging Research Center at UMBC} % Organization
    {Baltimore, MD} % Location
    {June 2016 - Aug. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Helped develop \href{https://retrieverstories.umbc.edu}{retrieverstories.umbc.edu}, a custom social media site for current/former students to share their experiences.  Developed new features using PHP, SQL, HTML, and CSS.}
      \end{cvitems}
    }

%  \cventry
%    {Assistant Programming Instructor} % Job title
%    {\href{https://blackrocket.com}{Black Rocket}} % Organization
%    {Harford Community College, MD} % Location
%    {May 2014 - Aug. 2014} % Date(s)
%    {
%      \begin{cvitems} % Description(s) of tasks/responsibilities
%        \item {Taught 3D modeling, game and web development at a kids technology summer 
%camp.  Planned and directly led the web development (programming) lessons as kids learned to make their first web page from scratch.}
%      \end{cvitems}
%    }

\end{cventries}
